---
title: "CSCI 385 Web Scraping Skeleton"
author: Joshua Vong
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(xml2)
```

1) (15 pts) Generate a single tibble including the best movies of all time, the best movies from 2020, and the best movies from 2019 according to Rotten Tomatoes ([https://www.rottentomatoes.com/top/](https://www.rottentomatoes.com/top/)). 

* Identify the URL's containing this information
* Use `rvest` to scrape these websites
* `bind_rows()` will help to combine tibbles for each "best of" list
* Convert the rating of each movie to a double
* Make sure there are no duplicate rows in the tibble

```{r}
# You may use this skeleton to get started if you would like but it is not required
rt <- tibble()
categories <- read_html("https://www.rottentomatoes.com/top/bestofrt/?year=2020") %>%
  html_nodes("#top_movies_main .articleLink") %>%
  html_text() %>%
  str_replace_all("[\n]+","")
categories

score1 <- read_html("https://www.rottentomatoes.com/top/bestofrt/?year=2020") %>%
  html_nodes("#top_movies_main .tMeterScore") %>%
  html_text()
  #str_replace_all("[\n]+","")
score1

movies <-read_html("https://www.rottentomatoes.com/top/bestofrt/?year=2019") %>%
  html_nodes("#top_movies_main .articleLink") %>%
  html_text() %>%
  str_replace_all("[\n]+","")
movies

score2 <- read_html("https://www.rottentomatoes.com/top/bestofrt/?year=2019") %>%
  html_nodes("#top_movies_main .tMeterScore") %>%
  html_text()
  #str_replace_all("[\n]+","")
score2
movies3 <- data.frame(categories,score1)
movies3
movies4 <- data.frame(movies,score2)
movies4
finaloutput <- bind_rows(movies3,movies4)
# Remove duplicate rows of rt
finaloutput[!duplicated(finaloutput), ]
finaloutput
# Use mutate to convert RatingTomatoMeter to double
finaloutput %>% 
  mutate(score1 = score1/100,score2/100)
rt # Print the tibble
```


2) (20 pts) Generate a tibble for the top 250 movies according to IMDB ([https://www.imdb.com/search/title/?groups=top_250&sort=user_rating,desc&start=1&ref_=adv_nxt](https://www.imdb.com/search/title/?groups=top_250&sort=user_rating,desc&start=1&ref_=adv_nxt)).

* Identify the URL's containing this information
* Use `rvest` to scrape these websites
* Use [https://selectorgadget.com/](SelectorGadget), Google developer tools in Chrome, or some other tool to help identify important CSS selectors
* This tibble should include movie `Rank`, `Title`, `Year`, `Rating`, and `Metascore`
* Not all movies on this list have a `Metascore`. Try using both `html_nodes()` and `html_node()` to correctly capture `NA` values 
* `add_row()` can be used to add rows to an existing tibble

```{r}
# You may use this skeleton to get started if you would like but it is not required
imdb <- tibble(Rank = integer(), Title = character(), Year = character(), Rating = double(), Metascore = double())
starts <- read_csv("https://www.imdb.com/search/title/?groups=top_250&sort=user_rating,desc&start=1&ref_=adv_nxt")
  
imdb.rank <- read_html("https://www.imdb.com/search/title/?groups=top_250&sort=user_rating,desc&start=1&ref_=adv_nxt") %>%
  html_nodes(".text-primary") %>%
  html_text() %>% as.integer()
  
  imdb.title <- read_html("https://www.imdb.com/search/title/?groups=top_250&sort=user_rating,desc&start=1&ref_=adv_nxt") %>% html_nodes(".lister-item-header a") %>% html_text()
  
  imdb.year <- read_html("https://www.imdb.com/search/title/?groups=top_250&sort=user_rating,desc&start=1&ref_=adv_nxt") %>% html_nodes(".text-muted.unbold") %>% html_text() %>% as.character()
  
  imdb.rating <- read_html("https://www.imdb.com/search/title/?groups=top_250&sort=user_rating,desc&start=1&ref_=adv_nxt") %>% html_nodes(".ratings-imdb-rating strong") %>% html_text() %>% as.double()
  
  imdb.metascore <-read_html("https://www.imdb.com/search/title/?groups=top_250&sort=user_rating,desc&start=1&ref_=adv_nxt") %>%
    html_node(".ratings-metascore") %>% html_text() %>% as.double()
  
  imdb <- add_row(imdb, Rank = imdb.rank, Title = imdb.title, Year = imdb.year, Rating = imdb.rating, Metascore = imdb.metascore)
imdb # Print the tibble
```


3) (5 pts) Create a column `TitleYear` in the IMDB tibble to match the format of titles in the Rotten Tomatoes tibble.

```{r}
imdb <- mutate(imdb, TitleYear = paste(imdb.title,imdb.year))
imdb # Print the tibble
```


4) (5 pts) Join the Rotten Tomatoes and IMDB tibbles together using `Title` and `TitleYear` as keys. Only keep rows with keys in both tibbles.

```{r}
moviesBoth <- left_join(imdb.title,finaloutput$categories,by = keys)
moviesBoth # PRINT THE TIBBLE
```


5) (5 pts) Generate a scatterplot of IMDB ratings versus Rotten Tomatoes ratings. Include a size aesthetic for `No. of Reviews` on Rotten Tomatoes. Are all points visible on this plot? If not, how can you make them visible?

```{r}
ggplot(data = imdb)+geom_point(aes(x = Rating, y = Rank))
ggplot(data = finaloutput)+geom_point(aes(x = score1, y =score2))
```

