---
title: "Assignment1"
author: "Joshua Vong"
date: "9/7/2021"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. (5 pts) Write a function sum_mults(nums, n) that returns the sum of all multiples of values in
the vector nums less than n. For example, sum_mults(c(3,5), 30) should return 195. Assume
that the elements of nums are positive integers.

```{r}
sum_mults <- function(nums, n){
  result <- 0
  sum <- 0
  for (i in 1:n-1) {
    for(num in nums){
      if(i %% num == 0){
        sum <- sum + i
        break
      }
    }
  }
  return(sum)
}

sum_mults(c(3,5),30)
sum_mults(c(2,8),40)
sum_mults(c(6,10),80)
```

2. Write a function collatz_len(n) that determines the first i for which
ai = 1 for a given n. For example, when n = 17, the sequence ai begins
17, 52, 26, 13, 40, 20, 10, 5, 16, 8, 4, 2, 1, . . .
1
and a13 = 1. Thus, collatz_len(17) should return 13.
```{r}
collatz <- function(n) {
  if ( n %% 2 == 0) {
    return(n/2)
  } else {
    return(3*n + 1)
  }
}

collatz_len <- function(n){
   numbers <- c() #vector being created to store n values
  while ( n != 1 ) {
    numbers <- c(numbers, n) # concatenate the n values together and store it in numbers
    n <- collatz(n) # call the collatz function to help
  }
  print(length(numbers))
}
collatz_len(17)
collatz_len(23)
collatz_len(39)
```

3. (5 pts) Write a function reverse(v) that reverses the vector v. So reverse(c(1,2,3)) should
return c(3,2,1). reverse should return NULL, not NA, when v is c().
```{r}
reverse <- function(v){
  newReverseList <- c()
  len <- length(v)
  j <- len
  if(len == 0)
    return(NULL)
  while(j != 0){
    for (i in 1:j) {
      newReverseList[i] <-v[j]
      j <- j-1
    }
  }
  print(newReverseList)
}
reverse(c(1,2,3))
reverse(c(6,2,6,7,2,5))
reverse(c(8,8,3,1,5,6,6,2))
```
4. (5 pts) Write a function drop(v, n) that drops every n
th element from the vector v.
drop(c(1,2,3,4,5), 2) should return c(1,3,5). drop should return NULL when n ≤ 1.
```{r}
drop <- function(v,n){
  remove <- n
  if(n <= 1){
    return(NULL)
  }
  for (i in v) {
    if(i == n)
      v <- v[! v %in% n]
  }
  print(v)
}
drop(c(1,2,3,4,5),2)
drop(c(6,2,5,1,19),3)
drop(c(21,34,7,99,15),5)
```
5. (10 pts) Write a function intersect_3(v, w, x) that returns a vector of the elements that appear
in each of the vectors v, w, and x. intersect_3(c(1,2,3,1), c(1,1,3,2), c(3,1,9,1)) should
return c(1,3).
```{r}
intersect_3 <- function(v,w,x){
  newIntersect <- c()
  for (i in 1:length(v)) {
    for (k in 1:length(w)) {
      if(v[i] == w[k]){
        for (j in 1:length(x)) {
          if(v[i] == x[j]){
            newIntersect <- c(newIntersect,x[j])
          }
        }
      }
    }
  }
  print(unique(newIntersect))
}
intersect_3(c(1,2,3,1), c(1,1,3,2), c(3,1,9,1))
intersect_3(c(7,25,3), c(7,1,66,25), c(5,7,93,13))
intersect_3(c(88,3,1), c(1,88), c(3,88,9,1,6,42,3))
```

6. (10 pts) Write a function filter_vec(v, p) that returns a vector containing all the elements of
v for which the predicate function p returns TRUE. For example,
  p <- function(x){ return(x>3) }
  l <- 1:6
  m <- filter_vec(l, p)
results in m being equal to the vector c(4,5,6). Make sure that filter_vec returns NULL when
p is FALSE for all elements of v.
```{r}
p <- function(x){return(x>3)}
l <- 1:6
q <- 1:3
o <- 1:13
filter_vec <- function(v,p){
  newList <- c()
  
  for (i in 1:length(v)) {
    functCall <- p(v[i])
    if(functCall == TRUE)
    {
      newList <- c(newList,v[i])
    }
  }
  print(newList)
}
m <- filter_vec(l,p)
r <- filter_vec(q,p)
y <- filter_vec(o,p)
```

7. (10 pts) Write a function n_fibs(n) that creates a vector of the first n Fibonacci numbers where
the first and second Fibonacci numbers are 1 (n_fibs(2) returns c(1,1))
```{r}
n_fibs <- function(n){
  len <- length(n)
  len[1:2] <- c(1,1) #first two are 1
  for(i in 3:n)
  {
    len[i] <- len[i-2] + len[i-1]
  }
  print(len)
}
n_fibs(4)
```


8. (15 pts) Write a function shift(v, n) that shifts the elements of a vector n places to the right. If
n is negative, the function should shift the vector to the left. For example, shift(c(1,2,3,4), 2)
should return c(3,4,1,2) while shift(c(1,2,3,4), -3) should return c(4,1,2,3). (Mod should be used)

```{r}
shift <- function(v,n){
   newList <- c()
   n <- n %% length(v)
   l <- c(v[(n+1):length(v)],v[1:n])
  for (i in v) {
    if(l <(n)){
      newList[(i+n)-l] <- v[i]
    }
    else
      newList[(i+n)] <- v[i]
  }
  print(newList)
}
shift(c(1,2,3,4), 2)
shift(c(1,2,3,4), -3)
shift(c(5,8,1,7), 3)
```

9. (20 pts) Write a function rem_consec_dups(v) that removes consecutive duplicates from the
vector v. rem_consec_dups(c(1,1,1,2,3,3,1,2,2)) should return c(1,2,3,1,2). Do not use
the built-in function rle in your solution.
```{r}
rem_consec_dups <- function(v){
  newList <- c()
  nextElement <- 1
  change <- 0
  for (i in v) {
    if(change != i){
      newList <- v[i]
      nextElement <- nextElement+1
    }
  }
  print(newList)
}
rem_consec_dups(c(1,1,1,2,3,3,1,2,2))
rem_consec_dups(c(1,1,6))
rem_consec_dups(c(1,1,6,6,1,6,2,54,2))
```
10. (20 pts) Write a function n_even_fibs(n) that creates a list of the first n even Fibonacci numbers.
The name of each value should be its position in the Fibonacci sequence as a string. For example,
n_even_fibs(5) should create a list with the structure
List of 5
  $ 3 : num 2
  $ 6 : num 8
  $ 9 : num 34
  $ 12: num 144
  $ 15: num 610
The toString function might be useful.
```{r}
n_even_fibs <- function(n){
  evenFib <- c()
  fib <- c()
  l <- 1
  str <- 1
  for(i in n) {
    if(l %% 2 == 0){
      evemFib[i] <- toString(str)
      fib[i] <-l
    }
    str <- str+1
    l <- l + 1
  }
  names(evenFib) <- evenFib
  return(evenFib)
  
  if(n == 0)
    return(NULL)
}
n_even_fibs(5)
n_even_fibs(10)
n_even_fibs(25)
```

